### 2013-09-18 mcmc.tex
measurements and outputs

@@

@@

For a committed probabilistic scientist---frequentist or
bayesian---there is no ``answer'', there are only probability density
functions.  Any time in a paper or in an email or in a conversation
we say what ``the answer is''---even if we say it with an error
bar---we have departed the probabilistic program.  There are many
principled ways to depart the program; in another \documentname, we
discuss the economic explanation of how we can make hard decisions in
the context of probabilistic reasoning\note{CITE DECISION DOCUMENT}.
But without going into the economic model, it is fair to say that a
substantial problem with being a committed probabilist is that when we
\emph{publish}, we are not permitted (not now, at least) to publish a
\emph{probability distribution over pubications}; we have to publish
\emph{one single, deterministic text}; we have to \emph{decide} what
to write in the title, the abstract, the tables, figures, and results
section.  Given a MCMC sampling of the posterior pdf, what do we
report as our \emph{results}?

...Reminder that a sampling is good for computing integrals (see above).
Therefore we should endeavor to use outputs that are based on integrals computed with the sampling.
This includes expectations and quantiles, but not optima...

...What should you report as the inferred parameter value and
associated uncertainty (error bar)?  What is an upper limit?  Do this
all for ONE DIMENSION.

>>>>

...What, briefly, is importance sampling?

@@

...What, briefly, is tempering?

@@

For a committed probabilistic scientist---frequentist or
bayesian---there is no ``answer'', there are only probability density
functions (pdfs).  Any time in a paper or in an email or in a conversation
we say what ``the answer is''---even if we say it with an error
bar---we have departed the probabilistic program.  There are many
principled ways to depart the program; in another \documentname, we
discuss the economic explanation of how we can make hard decisions in
the context of probabilistic reasoning\note{CITE DECISION DOCUMENT}.
But without going into that ``economic'' model, it is fair to say that a
substantial problem with being a committed probabilist is that when we
\emph{publish}, we are not permitted (not now, at least) to publish a
\emph{probability distribution over pubications}; we have to publish
\emph{one single, deterministic text}; we have to make a decision about what
to write in the title, the abstract, the tables, figures, and results
section.  Given a MCMC sampling of the posterior pdf, what do we
report as our \emph{results}?

One thing we can keep in mind to guide us in this is what we said above,
  which is that samplings are good for doing \emph{integrals}.
We should endeavor to use as our ``results'' outputs from the MCMC
  that are based on integrals computed with the sampling.
This includes expectations, medians, quantiles, one-dimensional histograms,
  and multi-dimensional histograms.
This does \emph{not} include the ``best'' sample or a mode or optimum.
The latter things are not necessarily illegitimate outputs of the MCMC,
  but they do not make best use of the fact that the sampling is a tool for integration,
  and we do not recommend them.

Imagine that you are in the simplest case:
You have a model with a small number of parameters (say three-ish),
  and only one of them is of great interest.
What are your options for the ``measurement'' of this parameter?
The only simple integral-based options are the posterior mean
  or posterior median value for the parameter.
\\HOGG CHOOSE NOTATION AND GIVE FORMULAE HERE.

What are your best options for the ``uncertainty'' or ``limits'' on this parameter?
The only simple integral-based options are posterior quantiles.
That is, the ``one-sigma'' error bar can be the size of the central (or smallest%
  \note{HOGG shizzle about choosing quantiles}) interval of the parameter that contains 68 percent of the posterior samples.
\\HOGG GIVE FORMULA HERE.\\
The ``two-sigma'' error bar would be the same but for the 95-percent interval.

One amusing thing is that if you choose the 68-percent interval sensibly,
  but use as the ``measurement'' the posterior mean,
  you can get pathological situations in which the posterior mean measurement
  is actually \emph{outside} the one-sigma confidence interval.
For this reason (and others), we usually recommend as a default behavior%
  ---in the one-dimensional case---%
  to choose the \emph{median} of sampling as the measurement value,
  the 16-percent quantile as the lower error bar,
  and the 84-percent quantile as the upper error bar.
This has pathologies in higher dimensions (as we are about to see),
  but is pretty safe for one-dimensional answers.

The conservative scientist would show not just 68-percent error bars,
  but also 95-percent
  (to help readers visualize the skew of the posterior pdf.
The very conservative scientist would also show a histogram
  of the posterior samples,
  with the relvant quantiles (2.5, 16, 50, 84, and 97.5~percent) indicated.

As we mentioned above, scientists often like to report the ``best sample'';
  that is, the sample with the highest posterior pdf value.
This is not usually a good idea.
For one, MCMC is a sampling algorithm, not an optimization algorithm;
  there are no guarantees that it will find the optimum of the posterior pdf in reasonable time.
For two, the closeness of the best sample to the posterior mode is a strong function of sample size.
For three, if you just want an optimum, use an optimizer!\note{HOGG, something?}
That is, we \emph{strongly advise against} reporting,
  as the measurement or among the results,
  the parameter value or values for the best sample.
